---
title: "linear_regression_on_50_startup_R"
output: html_document
---

## In this Task , we have predict the data on profit firstly we have a dataset of 50 startup companies and which have spends their money for R & D area, Admisnistration part and marketing spend in different different cities.

### Firstly, we load the data in the variable

```{r setup, include=FALSE}

library(readr)

startup_data <- read_csv("50_Startups.csv")

```
## we see the dataset

```{r }

head(startup_data)

```

## see the summary the dataset

```{r pressure, echo=FALSE}

summary(startup_data)

```
## we check if any colunms have null values and outliers so draw a graph

```{r}

par(mfrow = c(1,3))

boxplot(startup_data$`R&D Spend`)
boxplot(startup_data$Administration)
boxplot(startup_data$`Marketing Spend`)

```
## as we see our data is clean so we divide the dataset into two parts into train and test with the help of caTools


```{r}
library(caTools)

set.seed(10)

split_data <- sample.split(startup_data$Profit, SplitRatio = 0.75)
split_data

train <- subset(startup_data, split_data == T)
test <- subset(startup_data, split_data == F)

```

## create the model on the training dataset

```{r}

model <- lm(formula = Profit~., data = train)

summary(model)

```

## prediction 

```{r}

prediction <- predict(model, test)
prediction

```

## as we see the predict but we combinde both with the help of cbind and also add difference between actual profit and predict profit

```{r}

difference <- test$Profit - prediction

test <- cbind(test, prediction , difference)

head(test)

```

## as we see not a major difference between prediction and profit it just less the 12% so we just ignore less amount of difference. but also we find mean absolute percentage error

```{r}

mape <- mean(abs(difference)/test$Profit)
mape

```

## mape value is 2% is very low.














```






```{r}

```